---
title: "Incarceration Rates of Blacks vs. Whites"
author: "Asad Jaffery"
date: '2022-11-01'
output: html_document
---

```{r echo=FALSE, eval=TRUE, message=FALSE}
source("~/info201/assignments/a4-AsadJafferyy/source/a4-helpers.R")
source("~/info201/assignments/a4-AsadJafferyy/source/analysis.R")

```

## Abstract 
[TODO: Include a short abstract (about 50 words)]

# Test (TODO: Remove before submission!!)
```{r echo=FALSE}
q1_string <- test_query1()
num <- 5
```
As you know, this is a markdown report. The [R Markdown Cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf) is **useful!**

* Here's a test of a dynamic variable. Say **"`r q1_string`!!!** 
* Here's another test. A vector
* Another bullet point
* Another *special* bullet point
of numbers: `r test_query2(num)`.

Recall that _{r echo=TRUE}_ can be used to display the code, 
which is very useful when developing and debugging a report. Here's an example: 

```{r echo=TRUE}
num <- 5
sum <- sum(test_query2(num))
print(sum)
```

## Introduction 
[TODO]

## Data Summary 
This data examines `r num_counties` counties in the United States, and includes information that ranges from the year it was collected, and demographic of the population incarcerated, as well the total population. From this data, I was able to examine the county with the most black incarcerated individuals. This county happened to be the `r most_people_in_jail$county_name` in `r most_people_in_jail$year`. Then, I examined the `r most_people_in_jail$county_name` in order to find the ratio of black incarcerations to white incarcerations in 2018. This ratio ended up being `r la_black_white_ratio`. This number speaks for itself, and proves that there is some kind of systemic issue with the amount of black people being incarcerated. Lastly, I examined the average amount of white people who were incarcerated in every county and year that data was retrieved. This number is `r average_white_jail_pop`. The average amount of black people incarcerated in every county and year is `r average_black_jail_pop`. 

[TODO ... other sections ... See Canvas for details]

_All the very best with your work!_

